Verifying Demonstrations

### 2018-11-16 paper/intro.tex
restructures paper, informal models and properties, related work, formal definitions of protest, properties, adversary, then rest

\emph{Context.} 
Consider the following illustrative scenario.
Alice is an activist that organizes a protest in some location(s) against the current government, represented by Grace.
On the one hand, Alice wants to estimate the number of participants to prove a certain support for her cause.
On the other hand, Grace is an autocratic regime leader who opposes Alice's cause.
Bob, Carol and many others participate in the protest for Alice's cause against Grace.
However, they might only be willing to do so in a manner that does not leave any digital traces because of the fear of retribution against them from Grace's regime. 
To realize this objective, a reliable yet privacy-preserving crowd-counting mechanism is needed, which to the best of our knowledge is a problem that has not yet been entirely solved as of today.

@@

Finally, one important observation about crowd-counting that has not been adequately addressed in the design of current crowd-counting solutions is that it actually is an adversarial setting. 
Indeed, going back to our example, Alice the activist has an incentive to increase the tallied number of participants, whereas Grace (and possibly other entities) have an incentive to decrease it.
In this case, we are left with two options: either we trust Alice or Grace (or another third party) or we have to be able to verify their claims ourselves.
In this paper, our main objective is to provide a scheme preventing both Alice 
and Grace from cheating by providing verifiable claims.
To solve this issue, we need a verifiable participation count that can resist Sybil attacks while still preserving the participants' privacy to the extent possible given their physical presence at the protest. 
More precisely, our solution will not be able to magically prevent an observer (physically present or looking at photos or videos) from recognizing a particular individual at a protest. 
Nonetheless, we can ensure that none of the digital traces generated by a participant due to our scheme can be associated with their identity and that any witnessing is also unlinkable.
\seb{in the sentence above I am not sure that the word unlinkable will be 
  necessary clear}

@@

The paper is organized as follows.
First, in \cref{system-model}, we formalize the notion of protest and define the desired verifiability properties.
We also present our system as well as the adversary model together with desired privacy properties.
Next, in \cref{related-work}, we discuss related work in terms of these properties, first the crowd counting methods that are classically used and then work on location proof systems that inspired \CROCUS. 
In \cref{building-blocks}, we give the relevant background on the building blocks of our solution.
Afterwards in \cref{DB-anon-cred}, we present a new \ac{DB} version of the Schnorr protocol, different from that originally proposed by \textcite{DistanceBounding}.
We provide a proof of its security (\ie that fact that it achieved all desired \ac{DB} properties) 
%\daniel{Check that this is true before publication.} 
and formally verify it using Tamarin~\cite{TamarinDB}.
%Seb: we need to be careful about the above sentence
This version of the Schnorr protocol can then be used to do general \ac{DB} anonymous credentials.
Then \cref{Protocol}, we present \CROCUS, a privacy-preserving crowd counting estimation protocol constructed from these building blocks, before analyzing its security and privacy (\cref{SecurityAnalysis}).
Finally, we conclude with a discussion in \cref{Discussion} and future work in \cref{Conclusion}.
%\sonja{add (sub) sections for performance and verification}

>>>>

\emph{Context.} 
Consider the following scenario.
Alice is an activist that organizes a protest in some location(s) against the current government, represented by Grace.
On the one hand, Alice wants to estimate the number of participants to prove a certain support for her cause.
On the other hand, Grace is an autocratic regime leader who opposes Alice's cause.
Bob, Carol and many others participate in the protest for Alice's cause against Grace.
However, they might only be willing to do so in a manner that does not leave any digital traces because of the fear of retribution against them from Grace's regime. 
To realize this objective, a reliable yet privacy-preserving crowd-counting mechanism is needed, which to the best of our knowledge is a problem that has not yet been entirely solved as of today.

@@

Finally, one important observation about crowd-counting that has not been adequately addressed in the design of current crowd-counting solutions is that it actually is an adversarial setting. 
Indeed, going back to our example, Alice the activist has an incentive to increase the tallied number of participants, whereas Grace (and possibly other entities) have an incentive to decrease it.
In this case, we are left with two options: either we trust Alice or Grace (or another third party) or we have to be able to verify their claims ourselves.
In this paper, our main objective is to provide a scheme preventing both Alice 
and Grace from cheating by providing verifiable claims.
To solve this issue, we need a verifiable participation count that can resist Sybil attacks while still preserving the participants' privacy to the extent possible given their physical presence at the protest. 
More precisely, our solution will not be able to magically prevent an observer (physically present or looking at photos or videos) from recognizing a particular individual at a protest. 
Nonetheless, we have to ensure that none of the digital traces generated by a participant due to our scheme can be associated with their identity. % and that any witnessing is also unlinkable.
%\seb{in the sentence above I am not sure that the word unlinkable will be 
%  necessary clear}

@@

The paper is organized as follows.
First, in \cref{system-model}, we describe our system model and summarize the desired properties for crowd counting. Next, in \cref{related-work}, we discuss related work in terms of these properties, first the crowd counting methods that are classically used and then work on location proof systems that inspired \CROCUS. 
We then formalize the notion of protest and the desired verifiability and privacy properties, and in \cref{building-blocks}, we give the relevant background on the building blocks of our solution. 
Afterwards, in \cref{DB-anon-cred}, we present a new \ac{DB} version of the Schnorr protocol, different from that originally proposed by \textcite{DistanceBounding}.
We provide a proof of its security (\ie the fact that it achieved all desired \ac{DB} properties) 
\daniel{Check that this is true before publication.} 
and formally verify it using Tamarin~\cite{TamarinDB}.
\seb{we need to be careful about the above sentence}
%This version of the Schnorr protocol can then be used to do general \ac{DB} anonymous credentials.
Then in\cref{Protocol}, we present \CROCUS, a privacy-preserving crowd counting estimation protocol constructed from these building blocks, before analyzing its security and privacy (\cref{SecurityAnalysis}).
Finally, we discuss our assumptions and results \cref{Discussion} and give our conclusions in \cref{Conclusion}.
%\sonja{add (sub) sections for performance and verification}
